Cost-Benefit Analysis

### 2023-05-09 workflow/notebooks/cost-benefit-analysis.Rmd
Note NNB definitions

>>>>

- Number needed to screen (NNS) - the number of alerted patients the models must flag to identify 1 true positive. 
- Number needed to treat (NNT) - the number of true positive patients one must treat for 1 patient to benefit from the treatment.
- Number needed to benefit (NNB = NNS x NNT) - how many patients must be screened for 1 patient to benefit.
